Self Referencing Sequences

### 2014-10-26 draft.tex
started substitution rules

@@

The above analysis shows that, for example, the s

>>>>

The iterative process given in Section~\ref{iterativeprocess} is one way to generate self-referencing sequences. However, for certain generating sets $A$, there is a simpler ways to perform this iteration using a fixed set of substitution rules. Take $A = \{1,3\}$ as an example, and consider the sequence that starts with a 3:
\begin{align*}
333111333131333111333\dots
\end{align*}

@@
